---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRd6gPY3y4sbUCQonm7al3l3izO2Obztur_t3xGwrmIZ4_tNcZmN2QeLQHeoSuokzBUe7zYedECC91s/pub?gid=187295818&single=true&output=csv")

study_data <- logged_data %>%
  rename(
    study_location = `1. Where did the study session take place?`,
    start_time = `2. What time period did the study session start?`,
    study_purpose = `3. What was the main purpose of this study session?`,
    study_length = `4. How long was the study session in minutes?`
  ) %>%
  mutate(
    study_length = as.numeric(study_length)
  )

summary_min <- min(study_data$study_length, na.rm = TRUE)
summary_max <- max(study_data$study_length, na.rm = TRUE)
summary_mean <- mean(study_data$study_length, na.rm = TRUE)
total_sessions <- nrow(study_data)

location_plot <- ggplot(study_data, aes(x = study_location)) +
  geom_bar(fill = "skyblue") +
  labs(
    title = "Where Did UoA Students in My Sample Usually Study?",
    x = "Study Location",
    y = "Number of Study Sessions"
  ) +
  theme_minimal() +
  coord_flip()

purpose_plot <- ggplot(study_data, aes(x = study_purpose)) +
  geom_bar(fill = "coral") +
  labs(
    title = "Number of Study Sessions by Purpose",
    x = "Study Purpose",
    y = "Number of Study Sessions"
  ) +
  theme_minimal() +
  coord_flip()

time_plot <- ggplot(study_data, aes(x = start_time)) +
  geom_bar(fill = "mediumpurple") +
  labs(
    title = "When Do I Usually Start Studying?",
    x = "Time Period",
    y = "Number of Study Sessions"
  ) +
  theme_minimal() +
  coord_flip()

```


```{css}
body {
  font-family: Arial, sans-serif;
  line-height: 1.6;
  color: #4B0D57;
  background-color: #f5f7fa;
  padding: 24px;
}

h2, h3 {
  color: #4B7;
}

h2 {
  font-size: 2em;
  margin-bottom: 12px;
}

h3 {
  margin-top: 28px;
  border-left: 5px solid #6C8EBF;
  padding-left: 10px;
}

p {
  margin-bottom: 14px;
}

ul {
  background-color: #ffffff;
  border: 1px solid #d9e2f3;
  border-radius: 8px;
  padding: 16px 20px 16px 35px;
  margin-bottom: 22px;
}

pre {
  background-color: #FFF200;
  border-radius: 6px;
}

img {
  display: block;
  margin-top: 12px;
  margin-bottom: 12px;
  border: 1px solid #FFF200;
  border-radius: 8px;
  background-color: #ffffff;
  padding: 8px;
}
```

## Study Session Patterns

This dynamic report summarises the study session data I collected over time.

I recorded `r total_sessions` study sessions in total.

The average study session length was `r round(summary_mean, 1)` minutes.

The shortest study session was `r summary_min` minutes, and the longest was `r summary_max` minutes.

### Study location distribution

```{r}
print(location_plot)
```

This bar chart shows where I studied most often.

### Study purpose distribution

```{r}
print(purpose_plot)
```

This bar chart shows the most common purpose of my study sessions.
